---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Installation

To install `electricblue` use the following code:

```{r setup}
install.packages("devtools", "pacman")
devtools::install_github("daniel1noble/electricblue")
pacman::p_load(electricblue, tidyverse, stringr)
```

# How it works?
`electricblue` works directly with the .csv files downloaded directly from the data loggers. There is no need to change them in anyway before proceeding in R. The functions will process all the data and store it in a object. 

```{r load}
# Load the files by giving the path to the specific file you want to import into R using read_blue

data <- read_blue("./raw/04BC 0000 1C02 10-20240330 125652.csv")
```

The file provides you will the entire time series for the data logger, including the latitude and longitude with the serial number and unique name so that you can keep track of where the data came from. The object is of class `blue` and `dataframe`. This is convienient because functions can deal with this data quickly for you. For example, if we just want to plot we can now use the normal plot function with the data object:

```{r plot}
# Plot the temperature timeseries
  plot(data)
```
